\cvsection{Employment}

\begin{cventry}
    {AT\&T}
    {TDP Software Engineer Intern}
    {Jun. to Aug. 2021}
    {Java, Oracle, Bitbucket, Python, HTML/CSS, JavaScript}{Django, Pandas}
    \begin{cvitems}
        \item Devised an automated error detection module that identified anomalies with AT\&T's 5G location-based services, saving the company \$500,000
        % \item Consolidated \$500,000 by creating an automated error detection module that identifies anomalies with AT\&T's 5G location
        % \item Identified specific geo-validation in a database with 10000000 endpoints and aggregated specific use cases   
        \item Engineered a spelling proximity algorithm to correct errors with cell tower information which increased accuracy by 30\% using Java and Oracle
        \item Created HBOConnect, a prototype to engage user personalization, as an integration to HBOMax using Python/Django
    \end{cvitems}
\end{cventry}




\begin{cventry}
    {New Jersey Sustainability Reporting Hub}
    {Software Developer Intern}
    {Jun. to Aug. 2020}
    {HTML/CSS, JavaScript, AJAX, GitHub, REST API}{Bootstrap, D3.js}
    \begin{cvitems}
        \item Orchestrated and developed a strategic solution, MapSearchUI, to enhance the website experience, which was selected to be implemented for the company
        \item Refactored the prototype to a front-end application using JavaScript and D3.js, successfully integrating with the company's production stack
        % \item Improved the site's user experience by integrating an interactive searching tool, MapSearchUI, using JavaScript and D3.js
        % \item Created a New Jersey image map with links to county-specific archives using HTML
        \item Utilized the WordPress RESTful API to retrieve meta data  to display a dynamic pie chart of popular tags on the website
        % \item Enhanced MapSearchUI's user experience by incorporating a mobile view using D3.js to calculate the aspect ratio of the pie chart
    \end{cvitems}
\end{cventry}


\begin{cventry}
    {TCNJ Tutoring Center}
    {Computer Science Tutor}
    {Aug. 2019 to Aug. 2021}
    {}{}
    \begin{cvitems}
        \item Tutored college students in object-oriented programming, data structures, databases, algorithms, and software engineering

    \end{cvitems}
\end{cventry}

% \begin{cventry}
%     {Cygnus Professionals}
%     {Software Developer Intern}
%     {Jun. to Aug. 2019}
%     {Python, PostgreSQL, Bitbucket, Jira}{Psycopg2, NumPy, Matplotlib}
%     \begin{cvitems}
%       \item Designed an algorithm that displayed low inventory items in an analytics module of a consumer supplier management product using NumPy and Matplotlib
%       \item Integrated a Python script that dynamically updated the graphs after a database transaction using Matplotlib
%       \item Implemented PostgreSQL queries to populate and graph low inventory items
%     \end{cvitems}
% \end{cventry}

% \begin{cventry}
%     {Acrizen Technologies}
%     {Software Engineer}
%     {June 2016 to Nov. 2017}
%     {Java, GitHub}{}
%     \begin{cvitems}
%         \item Developed an attendance tracking module for a Learning Management System using Java
%         \item Integrated a grading system module using Java switch case
%     \end{cvitems}
% \end{cventry}

\begin{comment}
    \begin{cventry}
        {The College of New Jersey (TCNJ)}
        {Computer Science Department Tutor}
        {Apr. 2018 to May 2019}
        {Java, C++, C, Ruby, PostgreSQL, Regular Expressions}{Rails}
        \begin{cvitems}
            \item Tutoring TCNJ students in computer science coursework concerning topics such as object-oriented programming, data structures, discrete math, algorithms, computer architecture, operating systems, databases, and software engineering.
        \end{cvitems}
    \end{cventry}
\end{comment}

\begin{comment}
    \begin{cventry}
        {Mercer Street Friends}
        {Full Stack Web Developer}
        {Jan. to Feb. 2019}
        {Ruby, PostgreSQL, HTML, SCSS}{Rails, SendGrid}
        \begin{cvitems}
            \item Implemented a novel MVC full stack web application with \textsl{Ruby on Rails} and \textsl{PostgreSQL} for the Trenton-based non-profit organization, Mercer Street Friends, to effectively publicize the positive impacts of its charitable work.
            \item Applied the principles of responsive web design to provide a pleasant user experience on desktop, tablet, and mobile devices.
        \end{cvitems}
    \end{cventry}
\end{comment}
